% English string resources
% Header names
\newcommand{\strHeaderYandex}{Yandex LLC}
\newcommand{\strHeaderBootcamp}{Elbrus Coding Bootcamp}
\newcommand{\strHeaderFinancial}{Financial Information Systems}
\newcommand{\strHeaderEightPoints}{8 Points}
\newcommand{\strHeaderSibwaypro}{Sibwaypro}
\newcommand{\strHeaderUniversity}{Siberian State University of Telecommunications and Informatics}
\newcommand{\strName}{Eugene Maslovich}
% Sections
\newcommand{\strSectionExperience}{Experience}
\newcommand{\strSectionEducation}{Education}
\newcommand{\strSectionSkillsInterests}{Skills \& Interests}
% Labels
\newcommand{\strLabelProgrammingLanguages}{Favorite PLs}
\newcommand{\strLabelTech}{Tech}
\newcommand{\strLabelSpokenLanguages}{Spoken languages}
\newcommand{\strLabelInterests}{Interests}
% Roles
\newcommand{\strRoleYandex}{Senior Frontend Engineer}
\newcommand{\strRoleBootcamp}{Full-stack Web Development Coach}
\newcommand{\strRoleFinancial}{Senior Full-stack Engineer, Team Lead}
\newcommand{\strRoleEightPoints}{Lead Developer, Founder}
\newcommand{\strRoleSibwaypro}{Full-stack Web Developer}
% Locations
\newcommand{\strLocYandex}{Belgrade (Serbia), Moscow (Russia)}
\newcommand{\strLocBootcamp}{Moscow (Russia)}
\newcommand{\strLocFinancial}{Moscow, Novosibirsk (Russia)}
\newcommand{\strLocNovosibirsk}{Novosibirsk (Russia)}
% Bullets Yandex
\newcommand{\strYandexBOne}{Developed advertiser-facing frontend features for the Yandex Direct Ads platform (flagship product), delivering new UI workflows used daily by thousands of advertisers.}
\newcommand{\strYandexBTwo}{Implemented core modules in a newly launched marketplace management service, contributing from early design to release.}
\newcommand{\strYandexBThree}{Helped develop an internal employee evaluation tool (9-Box), creating frontend interfaces and backend APIs.}
% Bullets Bootcamp
\newcommand{\strBootcampBOne}{Taught full-stack web development (MERN stack), mentoring students, conducting code reviews, and designing teaching materials.}
\newcommand{\strBootcampBTwo}{Created internal tools to streamline class management and student progress tracking.}
% Bullets Financial
\newcommand{\strFinancialBOne}{Developed a collection management system that automated due payment tracking and improved operational efficiency for financial institutions.}
\newcommand{\strFinancialBTwo}{Built a low-code app constructor used to rapidly create CRM and banking applications, reducing development time and enabling business teams to configure workflows without deep technical expertise.}
\newcommand{\strFinancialBThree}{Ensured adherence to security standards and compliance requirements in banking software.}
% Bullets 8 Points
\newcommand{\strEightPointsBOne}{Founded and led a small web development company, managing a team and delivering projects for clients in Russia, Kazakhstan, and Germany.}
% Bullets Sibwaypro
\newcommand{\strSibwayproBOne}{Built and maintained a variety of websites for international clients.}
% Education
\newcommand{\strEducationDegree}{Master of Science in Computer Science}
% Skills lists
\newcommand{\strSpokenLanguagesList}{English (Upper-Intermediate), French (Elementary), Russian (Native)}
\newcommand{\strInterestsList}{Cyberpunk, Anime, PC \& Tabletop Games}
